The \dealii{} Library, Version 9.3

### 2021-06-17 9.3/paper.tex
updates introduction of sec 2.7

The source based installation of \dealii{} or
complex toolchains of multiple libraries working together with \dealii{}
can be done with the \candi{} script tool. \candi is a bash-script based tool,
it is the abbreviation of ``compile and install'' and it is released under the
GNU LGPL v3.0.
%
The origin of \candi{} is a fork made in 2013 from \texttt{dorsal},
a retired source based installer for the \texttt{FEniCS} library.
%
The \candi{} tool can be found via the download page of \dealii{} since version 8.5
and is under continuous and active maintenance. To install older releases of
\dealii{} toolchains one can checkout the branch corresponding to the
\dealii{}-version with \texttt{git}.

>>>>

The requirement to download, compile and install \dealii{} and its dependencies from
source is of mayor interest for many \dealii{}-users.
%
This can be of importance on arbitrary Linux-based operating systems for which
binary-install package aren't available or on compute clusters and other machines
without root privileges for the user to install system dependencies.

The source based installation of \dealii{} or complex toolchains of multiple libraries
working together with \dealii{} can be done with the \candi{} script tool for various
Linux operating systems, within the Windows Subsystem Linux (WSL) and on OSX (experimental).
%
The general assumption is that a C, C++ and Fortran compiler and suitable MPI-compilers
for the base compilers as well as the corresponding development system packages are
available.

\candi is a bash-script based tool, it is the abbreviation of ``compile and install''
and it is released under the GNU LGPL v3.0.
%
The origin of \candi{} is a fork made in 2013 from \texttt{dorsal},
a retired source based installer for the \texttt{FEniCS} library.
%
The \candi{} tool can be found via the download page of \dealii{} since version 8.5
and is under active maintenance.
To install older releases of \dealii{} toolchains one can checkout the branch
corresponding to the \dealii{}-version with \texttt{git}.
